---
title: "Lecture_6_Data_Manipulation"
output: html_document
---

```{r}
library(tidyverse)
options(tibble.print_min = 3) 
```
We’re going to be looking at a lot of output, so I’ll print only three lines of each tibble by default.


##Loading data 
```{r}
litters_data = read_csv("./data/FAS_litters.csv",
  col_types = "ccddiiii")
litters_data = janitor::clean_names(litters_data)

pups_data = read_csv("./data/FAS_pups.csv",
  col_types = "ciiiii")
pups_data = janitor::clean_names(pups_data)

view(litters_data)
```
##Select columns we care about, and rearrange column, rename columns
```{r}
select(litters_data, group, litter_number)
select(litters_data, group, starts_with("pups"))
rename(litters_data, GROUP=group)
relocate(litters_data, litter_number)
```

##Learning Check:Learning Assessment: In the pups data, select the columns containing litter number, sex, and PD ears.

```{r}
select(pups_data, litter_number, sex, pd_ears)
```

##pulling data
```{r}

pull(litters_data, group)
```

##filtering rows
we dont want certian data rows, how to filter it out and get rid of it
*use"==" as logical operation for equality testing
```{r}
filter(litters_data, gd_of_birth==20)
filter(litters_data, group=="Con7")
filter(litters_data, gd0_weight<23 )
filter(litters_data, pups_survive!=4)
filter(litters_data, group %in% c("Con7", "Con8"))
```

##Mutate 
Adding or change columns

```{r}
mutate(litters_data, 
       weight_change <-  gd18_weight - gd0_weight,
       group = str_to_lower(group))
```

##Arrange
```{r}
arrange(litters_data, gd_of_birth, gd0_weight)
```


##Pipes
Cleaning data
```{r}
litters_data_raw <- read_csv("data/FAS_litters.csv")
litters_clean_name <- janitor::clean_names(litters_data_raw)
litters_select <- select(litters_clean_name, group, pups_survive)
litters_filtered <- filter(litters_select, group=="Con7")
```
Below does the exactly the same thing but more organized
```{r}
litters_data <- 
  read_csv("data/FAS_litters.csv") %>%
  janitor::clean_names() %>%
  select(group, pups_survive) %>%
  filter(group =="Con7")
```

