---
title: "Simple document"
output: html_document
---

```{r}
library(tidyverse)
```

##Import some data 

We want to import 'FAS_litters.csv' . 

```{r}
litters_df <- read_csv("data/FAS_litters.csv")
```

Imported Data set, now want better names 
All variable names should be in case I prefer (snake_case)

opt-command-i to get code chunck
```{r}
names(litters_df)
litters_df <-  janitor::clean_names(litters_df)

```

Now we take a look at the data set.
Head function lets you print headings and the # after tell R how many rows

```{r}
print(litters_df)

head(litters_df, 20)
```

```{r, eval=FALSE}
view(litters_df)
```
^eval=false let markdown not evaluate the code chunk 

here is 'skimr': let you see key stats of data
```{r}
skimr::skim(litters_df)
```

##Arguments in 'read_csv'

look at help files

```{r}
litters_df <- 
  read_csv(
    "data/FAS_litters.csv",
    skip =5,
    col_name= FALSE,
    na="Low8")
  
```

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
```

